---
title: "1 Cluster Analysis of Perfect Order Data"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---


Observations / To do
--------------------
* Read fpc documentation
* Comment on whether clusters are similar to good or bad orders - do clusters match (or fit cleanly within) labels?
* Only an 80.8% agreement between the two methods.

```{r packages, echo=FALSE, warning=FALSE}
# Load necessary packages 

library(lattice)
library(ggplot2)
library(cluster)
library(NbClust)
library(mclust)
library(fpc)

#?kmeans()

```

```{r ImportData, echo=FALSE}
# Clear workspace and set working directory
rm(list = ls())
setwd("/Users/kbrooks/Documents/CS7641 Machine Learning/Assignment 3")

d = readRDS("models/Perfect_Order_cluster.rds") # scrubbed data set
#d_scaled = data.frame(scale(d))
#d_complete_scaled = readRDS("Perfect_Order_cluster_complete.rds")  # unscrubbed, fully scaled

set.seed(250)

```

Elbow Plot
----------
The elbow plot shows the decrease in within group sum of square errors as the number of clusters increase.  It is a quick and dirty means of evaluating a good number of clusters to use.  A good candidate for a natural number of clusters is directly after an elbow in the graph, showing, here, either 3 or 8 clusters. 


```{r Scree, warning=FALSE}
wssplot <- function(data, nc=15, seed=1234){
               wss <- (nrow(data)-1)*sum(apply(data,2,var))
               for (i in 2:nc){
                    set.seed(seed)
                    wss[i] <- sum(kmeans(data, centers=i, nstart = 1000)$withinss)}
                plot(1:nc, wss, type="b", xlab="Number of Clusters",
                     ylab="Within groups sum of squares")}
par(mfrow=c(1,1))
wssplot(d, nc=25)


dev.copy(png,'images/Perfect_Order_Elbow.png')
dev.off()

```

This analysis analyzes best cluster construction using the 26 indices provided in the _NbClust_ package [^fn-1] in R. _NbClust_ is tuned using the following parameters:

* minimum number of clusters
* maximum number of clusters
* method - the type of aggregation to uses.  Since were examining k-means, that is the aggregation method selected

[^fn-1]: Malika Charrad, Nadia Ghazzali, Veronique Boiteau, Azam Niknafs (2014). NbClust: An R Package for Determining the Relevant Number of Clusters in a Data Set. Journal of Statistical Software, 61(6), 1-36. URL http://www.jstatsoft.org/v61/i06/.

```{r NbClust, warning=FALSE}

nc <- NbClust(d, min.nc=2, max.nc=15, method="kmeans")
# warnings()
table(nc$Best.n[1,])

par(mfrow=c(1,1))
barplot(table(nc$Best.n[1,]), 
          xlab="Number of Clusters", ylab="Number of Criteria",
          main="Perfect Order Multi-Criterion Cluster Selection")

dev.copy(png,'Perfect_Order_bar.png')
dev.off()

```

Partition Clustering using K-means
----------------------------------

We implemented K-means using the native kmeans() method within R using the Hartigan-Wong[^fn-2] algorithm. Kmeans() is tuned using the following parameters:

* Number of clusters
* Maximum number of iterations (defaults to 10)
* Number of starts (default = 1)...do more
* Algorithm (default is Hartigan-Wong)

[^fn-2]: Hartigan, J. A. and Wong, M. A. (1979). A K-means clustering algorithm. Applied Statistics 28, 100–108.


```{r KMeans, warning=FALSE}
fit.km.3 <- kmeans(d, 3, nstart=25) 
#fit.km.8 <- kmeans(d, 8, nstart=25) 

saveRDS(fit.km.3, "models/Perfect_Order_KM_3_model.rds")
#saveRDS(fit.km.8, "Perfect_Order_km8_model.rds")
?table

table(fit.km.3$cluster)

fit.km.3$size
#fit.km.8$size
 
fit.km.3$centers
 #fit.km$cluster

aggregate(d, by=list(cluster=fit.km.3$cluster), mean)

# transpose and print this to see what's significant

```

Hierarchical Agglomerative Clustering
-------------------------------------

This analysis implements Ward's heirarchical agglomerative clustering criterion using the hclust() method in the _cluster_ package[^fn-3] in R. hclust() is tuned using the following parameters:

* Manhattan distance
* Agglomeration method: ward.D2 method is used to minimize variance and find compact, spherical clusters.


[^fn-3]: Murtagh, F. and Legendre, P. (2013). Ward's hierarchical agglomerative clustering method: which algorithms implement Ward's criterion? _Journal of Classification_.

```{r HierAgglom, warning=FALSE}
# ?hclust()
par(mfrow=c(1,1))
distance <- dist(d, method = "manhattan") # distance matrix
fit.hc <- hclust(distance, method="ward.D2") 
saveRDS(fit.hc, "Perfect_Order_hc_model.rds")
plot(fit.hc, labels=FALSE) # display dendogram
groups <- cutree(fit.hc, k=2) # cut tree into 3 clusters
# draw dendogram with red borders around the 3 clusters 
rect.hclust(fit.hc, k=2, border="red")
dev.copy(png,'Perfect_Order_HAC.png')
dev.off()

```

Model Based Clustering
----------------------
This analysis implements the optimal model according to the Bayes Information Criterion (BIC) for Expectation Maximization (soft) clustering using the _mclust_ package[^fn-4][^fn-5] in R. _Mclust_ is tuned via:

* model type (based on BIC)
* The number of clusters for which the BIC is to be calculated (here set at the number of features)

Observations / Questions
------------------------
* What is the best model type?
* What is the recommended number of clusters?
* Do they differ from either k-means or hierarchical agglomerative

[^fn-4]:Chris Fraley, Adrian E. Raftery, T. Brendan Murphy, and Luca Scrucca (2012) mclust Version 4 for R: Normal Mixture Modeling for Model-Based Clustering, Classification, and Density Estimation Technical Report No. 597, Department of Statistics, University of Washington

[^fn-5]:Chris Fraley and Adrian E. Raftery (2002) Model-based Clustering, Discriminant Analysis and Density Estimation, _Journal of the American Statistical Association_, 97:611-631

```{r EMCluster, warning=FALSE}
# Model Based Clustering
library(mclust)
# ?Mclust()
# fit.em <- Mclust(d)
fit.em <- Mclust(d, modelNames = c("EII", "VII", "EEI", "EVI", "VEI", "VVI"), G=1:50)
#fit.em <- Mclust(d, G=3)

dSummary <- summary(fit.em, data = d)
dSummary
names(dSummary)

saveRDS(fit.em, "Perfect_Order_EM_model.rds")

par(mfrow=c(1,1))
plot(fit.em, what="BIC") # plot results 
dev.copy(png,'images/Perfect_Order_EM.png')
dev.off()

summary(fit.em) # display the best model

```

Fit EM-3 Model
--------------

```{r EM3}
fit.em.3 <- Mclust(d, G=3)
saveRDS(fit.em.3, "models/Perfect_Order_EM_3_model.rds")
summary.em.3 <- summary(fit.em.3, data = d)

# EM summary
table(summary.em.3$classification)

# k-means summary
table(fit.km.3$cluster)

# k-means versus EM
table(fit.km.3$cluster, summary.em.3$classification)
```

Compare KM-3 and EM-3
---------------------

```{r}

fit.em.3 = readRDS("models/Perfect_Order_EM_3_model.rds")
fit.km.3 = readRDS("models/Perfect_Order_KM_3_model.rds")

summary.em.3 <- summary(fit.em.3, data = d)
# EM summary
table(summary.em.3$classification)

# k-means summary
table(fit.km.3$cluster)

# k-means versus EM
table(fit.km.3$cluster, summary.em.3$classification)


# 80.8 % agreement
```

Plotting Cluster Solutions
--------------------------
This analysis utilizes the _cluster_[^fn-6] and _fpc_[^fn-7] packages in R. 

[^fn-6]: Maechler, M., Rousseeuw, P., Struyf, A., Hubert, M., Hornik, K.(2014). cluster: Cluster Analysis Basics and Extensions. R package version 1.15.2.
[^fn-7]: Christian Hennig (2014). fpc: Flexible procedures for clustering. R package version 2.1-9. http://CRAN.R-project.org/package=fpc

```{r ClusterPlots, warning=FALSE}
d = readRDS("models/Perfect_Order_cluster.rds")
fit.km.3 = readRDS("models/Perfect_Order_KM_3_model.rds")
fit.em.3 = readRDS("models/Perfect_Order_EM_3_model.rds")

# KM3 Cluster Plot against 1st 2 principal components
library(cluster) 

par(mfrow=c(1,1))
clusplot(d, fit.km.3$cluster, color=TRUE, shade=TRUE, 
     lines=0, main = "K-Means Cluster Plot")
dev.copy(png,'images/Perfect_Order_KM_plot.png')
dev.off()

# EM3 Cluster Plot against 1st 2 principal components

par(mfrow=c(1,1))
clusplot(d, fit.em.3$classification, color=TRUE, shade=TRUE, 
     lines=0, main = "EM Cluster Plot")
dev.copy(png,'images/Perfect_Order_EM_plot.png')
dev.off()

```

Validating Cluster Solutions
----------------------------

```{r Validating, warning=FALSE}
# comparing 2 cluster solutions
library(fpc)
cluster.stats(d, fit.km.3$cluster, fit.em$cluster)
```

Simplified Clusters with no Indicator Variables
-----------------------------------------------
```{r numericOnly, warning=FALSE}

str(d)
d.numeric = dplyr::select(d, LineCount, Units)
#wssplot(d.numeric)

#nc.numeric <- NbClust(d.numeric, min.nc=2, max.nc=15, method="kmeans")
# warnings()
#table(nc.numeric$Best.n[1,])

# par(mfrow=c(1,1))
# barplot(table(nc.numeric$Best.n[1,]), 
#           xlab="Number of Clusters", ylab="Number of Criteria",
#           main="Numeric Variables Multi-Criterion Cluster Selection")

fit.km.num.3 <- kmeans(d, 3, nstart=25) 

fit.em.num.3 = Mclust(d, modelNames = c("EII", "VII", "EEI", "EVI", "VEI", "VVI"), G=3)

em.num.3.Summary <- summary(fit.em.num.3, data = d)

# k-means versus EM
table(fit.km.num.3$cluster, em.num.3.Summary$classification)

(3345 + 65) / 4420
```

Overlap with Labels
-------------------

```{r LabelsVsClusters}

d.with.labels = readRDS("models/Perfect_Order_cluster_with_labels_d.rds")
fit.km.3 = readRDS("models/Perfect_Order_KM_3_model.rds")
fit.em.3 = readRDS("models/Perfect_Order_EM_3_model.rds")

# kmeans
table(d.with.labels$Outcome, fit.km.3$cluster)

# EM
table(d.with.labels$Outcome, fit.em.3$classification)
```



```{r clusterTiming}

library(mclust)
library(microbenchmark)

d = readRDS("models/Perfect_Order_cluster.rds")

KMtrainingTime = microbenchmark(
    trashKM <- kmeans(d, 3, nstart=25), 
    times = 10L)

cat("k-means mean training time:", KMtrainingTime$time[3]/1000000000, "ns")

EMtrainingTime = microbenchmark(
    trashEM <- Mclust(d, G=3), 
    times = 10L)

cat("EM mean training time:", EMtrainingTime$time[3]/1000000000, "ns")
```
