---
title: "2a Principal Components Analysis of Perfect Order Data"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---

To Do
-----
* Read FactoMineR documentation and tutorial
* try running this against raw data (all 45 variables)
* Bar chart of eigenvalues
* interpretation of circle chart

Observations
------------
* It takes 15 components to get to 80% of the variance

```{r packages, warning=FALSE}
# Load necessary packages 

library(FactoMineR)
library(lattice)
library(ggplot2)
library(caret)
library(microbenchmark)

```

```{r ImportData, echo=FALSE}
# Clear workspace and set working directory
rm(list = ls())
setwd("/Users/kbrooks/Documents/CS7641 Machine Learning/Assignment 3")
par(mar = c(0, 0, 0, 0))

d = readRDS("models/Perfect_Order_cluster.rds")

set.seed(250)
```

Principal Components Analysis
-----------------------------

This analysis implements PCA using the _FactoMineR_ package in R[^fn-1]. _FactoMineR_ is tuned using the following parameters:

* X - a data frame with n rows (individuals) and p columns (numeric variables)
* ncp	- number of dimensions kept in the results (by default 5)
* scale.unit	- a boolean, if TRUE (value set by default) then data are scaled to unit variance
* ind.sup	- a vector indicating the indexes of the supplementary individuals
* quanti.sup - a vector indicating the indexes of the quantitative supplementary variables
* quali.sup	- a vector indicating the indexes of the categorical supplementary variables
* row.w	- an optional row weights (by default, a vector of 1 for uniform row weights)
* col.w	- an optional column weights (by default, uniform column weights)
* graph	- boolean, if TRUE a graph is displayed
* axes - a length 2 vector specifying the components to plot


[^fn-1]: Francois Husson, Julie Josse, Sebastien Le and Jeremy Mazet (2015). FactoMineR: Multivariate Exploratory Data Analysis and Data Mining. R package version 1.29. http://CRAN.R-project.org/package=FactoMineR

```{r runpca, warning=FALSE}

# ?PCA()

res.pca = PCA(d, scale.unit=TRUE, ncp=15, graph=T)

dev.copy(png,'Perfect_Order_pca.png')
dev.off()

saveRDS(res.pca, "models/Perfect_Order_pca_model.rds")

res.pca
# names(res.pca)
res.pca$eig
# res.pca$ind # distance
res.pca$ind.sup
res.pca$var
res.pca$quali.sup
res.pca$quanti.sup

```

Plots

```{r}
library("factoextra")
fviz_screeplot(res.pca, ncp=15)

dev.copy(png,'images/Perfect_Order_pca_scree.png')
dev.off()

# Contributions of variables on PC1
fviz_pca_contrib(res.pca, choice = "var", axes = 1)

dev.copy(png,'images/Perfect_Order_pca_var_contrib.png')
dev.off()
```

```{r PCATiming}

library(FactoMineR)
library(microbenchmark)

d = readRDS("models/Perfect_Order_cluster.rds")

trainingTime = microbenchmark(
    res.pca = PCA(d, scale.unit=TRUE, ncp=15, graph=F), 
    times = 10L)

cat("Mean training time:", trainingTime$time[3]/1000000000, "ns")
```

